% Please do not change the document class
\documentclass{scrartcl}

% Please do not change these packages
\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}
\usepackage{setspace}
\doublespace

% You may add additional packages here
\usepackage{amsmath}

% Please include a clear, concise, and descriptive title
\title{Continuing Personal Development Report}

% Please do not change the subtitle
\subtitle{COMP160 - CPD Report}

% Please put your student number in the author field
\author{1603748}

\begin{document}

\maketitle

\section*{Introduction}
In the future after I complete this course my goal is to become a game developer. I would like to start small and make indie games in a small development team, then If things go well I would love to join a larger company to work on AAA games as a computing professional. This term the five key challenges I faced were problem solving, essay time management, communication and coordination, hardware, and version control. I will highlight these five skills in my report by acknowledging the difficulties i faced then suggesting how i will overcome the obstacle in relation to a SMART action. 

\section{Problem solving}
Problem solving is a highly important and useful skill to have, especially when working in the games industry. Being able to solve problems when programming games without having to seek help is an essential skill. During this semester I have found it very challenging to find solutions to my problems without looking online for help. I would like to improve this in future by spending more time problem solving rather than giving up and searching for answers. To develop my problem solving skills further I will spend a few hours a week programming without any help form elsewhere which will force me to solve any problems I face myself. 

\section{Essay Time Management}
Time management is a vital skill to master as it will makes getting tasks done much easier and also prevents you from rushing work which can result in lower quality work. It is particularly useful when writing essays, rather than waiting until there is only a week left, it is better to write essays in chunks. This is something I have struggled with, both this term and last term, I tend to leave all my essay assignments very late and do the whole essay within a few days. I would like to improve on this next academic year by setting myself an amount of hours to spend working on my essays each week, this way I will be working on my essay right from the day its set to the day it is due. 

\section{Communication and Coordination}
In the game industry you are always working in a team, whether it is a very large team with a known company or a small indie team. This means that communication and coordination with that team is indispensable as everyone in the team needs to know what everyone else is doing. In the small teams we have been working in this term it has been very important to let everyone else know what you were working on because it avoids conflicting versions when multiple team members work on the same thing. This was a problem my team had this term, there were a few times that multiple people were working within the actual level in engine at the same time which caused a lot of problems, including myself redoing all the work I had already done. To alleviate this next year, whenever I am working on the game I will inform my team exactly what I am doing to avoid conflicting versions.  

\section{Learning and practicing new skills}
As technology advances new software and hardware becomes the standard to use when developing games. Being able to adapt quickly to these changes and learn new skills is very useful. During this term there has been lots of new skills to learn, some of which I found fairly easy to get the hang of, but some were a lot harder to learn than others. For example I found learning to use the arduino was very challenging, most likely because I had not worked with hardware in the past. Learning C++ was also a challenge for me as it was a big step up from the kind of programming language that I am used to. I eventually became fairly good at using the arduino and C++, however I believe that if I spent more time practicing and learning these new skills I could have significantly improved the quality of some of my assignments. I will improve my practicing and learning in future by spending a few extra hours on weekends practicing necessary new skills such as a new programming language and engine if I use unity next year.  

\section{Version Control}
Version control is use massively in the games industry an is something that any game developer should master. Last term I learnt the basics of version control and It was also one of my key skills as I found it challenging to use at first, particularly branching. This term I have learnt the importance of informing the rest of your team of what you are working on to avoid, what I would call a version control disaster. In the last week before the content lock our whole team were working hard on the game, but we didn't tell each other what we were working on, which resulted in 3 versions of the same level. Learning to use svn rather than github which I was used to after using it the first term was also quite a challenge at first. Next year I plan to learn from my previous mistakes and master my version control skills to avoid another version control disaster like I had this year. I will ensure my team uses version control efficiently by reminding myself and my team to inform the rest of the team on what they are working on. 

\section*{Conclusion}
In my report I have identified 5 key skills I have found challenging this term and have suggested how I will improve this skills and overcome the obstacles I have encountered this term. By doing the tasks I have set myself in this report I will improve these skills and hopefully become a more professional game developer for next year and for the rest of my future career. 

\bibliographystyle{ieeetran}
\bibliography{references}

\end{document}
